Reply to comment by R.~Klein on ``Adaptive Resolution Simulation in Equilibrium and Beyond''

### 2015-06-15 writeDown/pub.epj/comment.klein.reply/main.tex
revise

We assume that the interactions between particles are pairwise, and denote
the energy contribution of one particle pair by $u(r)$, with $r$ being the distance
between the particles. Cuting-off this interaction means that it is assumed to vanish
if the distance between the particles is larger than the cut-off radius $r_c$.
``The correlation between the atomistic and the coarse-grained
regions is negligible'' means that the
degrees of freedom (positions and velocities) of two particles
in the atomistic and the coarse-grained regions, respectively, are almost un-correlated.

It is true that by introducing the adaptive resolution, the system is not homogeneous
and isotropic anymore. Therefore, strictly speaking the standard definition
of RDF's and 3-body correlation functions is problematic. However, if the configuration
of the coarse-grained and the
hybrid regions are designed with high accuracy, one can approximately
treat the system as homogeneous and isotropic, and the RDF and 3-body correlation
are well-defined for (at least) the center-of-mass configuration of water system.
On the other hand, if the coarse-grained or hybrid
configuration deviates from the full-atomistic reference,
one can anyway compute the RDF,
which is the averaged structure around a particle, and contains information on
the difference to the
full-atomistic reference (probably with positive-negative cancellation).
\redc{In practice,
the deviating RDFs is to improve the accuracy of AdResS,} and a
satisfactory accuracy of RDF and 3-body correlation is achieved by
using a fully converged RDF correction force in
AdResS~\cite{wang2012adaptive,wang2013grand}.

@@

\paragraph{Structure of the hybrid zone}
The major difference between a phase coexisting system and an AdResS
system is that the former satisfies both the momentum and energy
conservations, while the later can satisfy only one of the two.
It would be very interesting to establish an analogue between
both the systems, however one must pay attention
to this difference that may play a significant role in the final conclusions.

>>>>

We assume that the interactions between particles are pairwise, and denote
the energy contribution of one particle pair by $u(r)$, with $r$ being the distance
between the particles. Cutting-off this interaction means that it is assumed to vanish
if the distance between the particles is larger than the cut-off radius $r_c$.
``The correlation between the atomistic and the coarse-grained
regions is negligible'' means that the
degrees of freedom (positions and velocities) of two particles
in the atomistic and the coarse-grained regions, respectively, are almost un-correlated.

It is true that by introducing the adaptive resolution, the system is not homogeneous
and isotropic anymore. Therefore, strictly speaking, the standard definition
of RDF's and 3-body correlation functions is problematic. However, if the configuration
of the coarse-grained and the
hybrid regions are designed with high accuracy, one can approximately
treat the system as homogeneous and isotropic, and the RDF and 3-body correlation
are well-defined for (at least) the center-of-mass configuration of water system.
On the other hand, if the hybrid
configuration deviates from the full-atomistic reference,
one can anyway compute the RDF,
which is the averaged anisotropic structure around a particle, and contains information on
the difference to the
full-atomistic reference (probably with positive-negative cancellation).
In practice,
it has been shown that this information is sufficient for computing
a RDF correlation that drives the system
to the correct RDF in the hybrid region~\cite{wang2012adaptive,wang2013grand}.

% it has been shown that  
% the RDF correlation can be effectively computed by using
% this averaged RDF.

@@

\paragraph{Structure of the hybrid zone}
It would be very interesting to establish an analogue between
a phase coexisting system
and an AdResS system.
We would like to note that the major difference between them
is that the former satisfies both the momentum and energy
conservations, while the latter can satisfy only one of the two.
This difference may play a significant role in deriving the final conclusions.
